---
title: "TD1 Assignment Report"
author: "Your Name"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1: Demand Curve

## Background

We simulate a market of 1000 consumers, where each consumer's reservation price is randomly distributed between 0 and 1. The demand curve shows the relationship between market price and quantity demanded.

## Simulation

### Demand Function

```{r demand-function}
# Number of consumers
N <- 1000
# Generate random reservation prices
reservation_prices <- runif(N)

# Generate market prices
market_prices <- seq(0, 1, by = 0.01)

# Calculate quantity demanded for each market price
quantity_demanded <- sapply(market_prices, function(p) sum(reservation_prices >= p))
```

### Plot

```{r demand-plot}
# Plot demand curve
plot(quantity_demanded, market_prices, type = "l", col = "blue", lwd = 2,
     xlab = "Quantity Demanded", ylab = "Market Price",
     main = "Demand Curve")
```

### Alternative Representation

```{r sorted-demand}
# Sort reservation prices in descending order
sorted_reservation_prices <- sort(reservation_prices, decreasing = TRUE)

# Create fraction of population
fraction_population <- seq(1 / N, 1, by = 1 / N)

# Plot sorted reservation prices against fraction of population
plot(fraction_population, sorted_reservation_prices, type = "l", col = "red", lwd = 2,
     xlab = "Fraction of Population", ylab = "Reservation Price",
     main = "Sorted Demand Curve")
```

# Exercise 2: Monopoly Pricing

## Background

We simulate a monopolist's pricing problem, where each day's buyers have reservation prices distributed uniformly on (0,1). The firm's goal is to maximize profits.

## Simulation

### Profit Function

```{r monopoly-simulation}
# Number of buyers per day
daily_buyers <- 100
# Marginal cost
c <- 0.2
# Simulate profits at different prices
prices <- seq(0.1, 0.9, by = 0.1)
profits <- sapply(prices, function(p) {
  quantity <- sum(runif(daily_buyers) >= p)
  revenue <- p * quantity
  cost <- c * quantity
  revenue - cost
})
```

### Plot

```{r monopoly-plot}
# Plot profits against prices
plot(prices, profits, type = "b", col = "green", pch = 19, lwd = 2,
     xlab = "Price", ylab = "Profit", main = "Profit as a Function of Price")
```

# Exercise 3: Duopoly and Demand Estimation

## Background

We estimate the Cournot duopoly equilibrium using a linear demand function.

## Simulation

### Simulated Observations and Regression

```{r duopoly}
# Simulation parameters
nsim <- 1000
beta_x <- 1.5
beta_q <- -1
beta_g <- 0.6

# Simulate variables
X <- rnorm(nsim, mean = 10, sd = 2)
w <- rnorm(nsim, mean = 2, sd = 1)
epsilon_D <- rnorm(nsim, mean = 0, sd = 4)
epsilon_S <- rnorm(nsim, mean = 0, sd = 1)

# Demand function: P = beta_x * X + beta_q * Q + epsilon_D
Q <- seq(0, 100, length.out = nsim)
P <- beta_x * X + beta_q * Q + epsilon_D

# Naive regression
model_naive <- lm(P ~ Q)
plot(Q, P, pch = 16, col = "blue", main = "Naive Regression: Price vs. Quantity")
abline(model_naive, col = "red", lwd = 2)

# Instrumental Variables (IV) Regression
library(AER)
iv_model <- ivreg(P ~ Q | X + w)
summary(iv_model)
```

