---
title: "TD1 Assignment Report"
author: "DRAME Alia MEIGNEN Erwan LAKAS Idriss"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1: Demand Curve

## Background

We simulate a market of 1000 consumers, where each consumer's reservation price is randomly distributed between 0 and 1. The demand curve shows the relationship between market price and quantity demanded.

## Simulation

### Demand Function

```{r demand-function}
# Number of consumers
N <- 1000
# Generate random reservation prices
reservation_prices <- runif(N)

# Generate market prices
market_prices <- seq(0, 1, by = 0.01)

# Calculate quantity demanded for each market price
quantity_demanded <- sapply(market_prices, function(p) sum(reservation_prices >= p))
```

### Plot

```{r demand-plot}
# Plot demand curve
plot(quantity_demanded, market_prices, type = "l", col = "blue", lwd = 2,
     xlab = "Quantity Demanded", ylab = "Market Price",
     main = "Demand Curve")
# Comment: The demand curve shows how market price decreases as quantity demanded increases, reflecting typical consumer behavior in response to price changes.
```

### Alternative Representation

```{r sorted-demand}
# Sort reservation prices in descending order
sorted_reservation_prices <- sort(reservation_prices, decreasing = TRUE)

# Create fraction of population
fraction_population <- seq(1 / N, 1, by = 1 / N)

# Plot sorted reservation prices against fraction of population
plot(fraction_population, sorted_reservation_prices, type = "l", col = "red", lwd = 2,
     xlab = "Fraction of Population", ylab = "Reservation Price",
     main = "Sorted Demand Curve")
# Comment: This plot illustrates the distribution of reservation prices, showing how the fraction of the population willing to pay decreases as the price increases.
```

# Exercise 2: Monopoly Pricing

## Background

We simulate a monopolist's pricing problem, where each day's buyers have reservation prices distributed uniformly on (0,1). The firm's goal is to maximize profits.

## Simulation

### Profit Function

```{r monopoly-simulation}
# Number of buyers per day
daily_buyers <- 100
# Marginal cost
c <- 0.2
# Simulate profits at different prices
prices <- seq(0.1, 0.9, by = 0.1)
profits <- sapply(prices, function(p) {
  quantity <- sum(runif(daily_buyers) >= p)
  revenue <- p * quantity
  cost <- c * quantity
  revenue - cost
})
```

### Plot

```{r monopoly-plot}
# Plot profits against prices
plot(prices, profits, type = "b", col = "green", pch = 19, lwd = 2,
     xlab = "Price", ylab = "Profit", main = "Profit as a Function of Price")
# Comment: The profit curve peaks at an optimal price, where the balance between price and quantity sold maximizes revenue minus cost. Beyond this point, raising the price reduces profits as the reduction in quantity sold outweighs the higher price per unit.
```

# Exercise 3: Duopoly and Demand Estimation

## Background

We estimate the Cournot duopoly equilibrium using a linear demand function.

## Simulation

### Simulated Observations and Regression

```{r duopoly}
# Simulation parameters
nsim <- 1000
beta_x <- 1.5
beta_q <- -1
beta_g <- 0.6

# Simulate variables
X <- rnorm(nsim, mean = 10, sd = 2)
w <- rnorm(nsim, mean = 2, sd = 1)
epsilon_D <- rnorm(nsim, mean = 0, sd = 4)
epsilon_S <- rnorm(nsim, mean = 0, sd = 1)

# Demand function: P = beta_x * X + beta_q * Q + epsilon_D
Q <- seq(0, 100, length.out = nsim)
P <- beta_x * X + beta_q * Q + epsilon_D

# Naive regression
model_naive <- lm(P ~ Q + X + w)  # Simple regression without AER
summary(model_naive)

# Plot the results
plot(Q, P, pch = 16, col = "blue", main = "Naive Regression: Price vs. Quantity")
abline(model_naive, col = "red", lwd = 2)
```
