---
title: "TP2 - Survival Analysis and Social Networks"
author: "DRAME Alia LAKAS Idriss MEIGNAN Erwan "
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

This document investigates the impact of social networks on the adoption of an instant messenger using survival analysis methods. The datasets `messenger_adoption.csv` and `users_socnet.csv` are used to analyze how demographic and network characteristics influence adoption decisions.

# Data Loading

```{r load-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(survival)
library(survminer)
library(igraph)

# Load the datasets
d1 <- read.csv("messenger_adoption.csv")
edgelist <- read.csv("users_socnet.csv")

# Create necessary variables
d1 <- d1 %>% 
  mutate(status = !is.na(time),
         time = ifelse(is.na(time), 300, time),
         sex = ifelse(sex == 0, "female", "male"))

g1 <- graph.data.frame(edgelist, directed = FALSE, vertices = d1)
```

# Descriptive Analysis

```{r descriptive-analysis}
# Descriptive statistics
d1 %>% summary()

# Distribution of adoption times
ggplot(d1, aes(x = time, fill = status)) +
  geom_histogram(binwidth = 10, alpha = 0.7) +
  theme_minimal() +
  labs(title = "Adoption Time Distribution", x = "Time (days)", y = "Number of Users")
```

# Kaplan-Meier Estimation

```{r kaplan-meier}
# Kaplan-Meier object creation
km_obj <- survfit(Surv(time, status) ~ sex, data = d1)

ggsurvplot(km_obj, data = d1, pval = TRUE, conf.int = TRUE,
           title = "Kaplan-Meier Survival Curves by Sex",
           legend.title = "Sex",
           xlab = "Time (days)", ylab = "Survival Probability")
```

# Cox Model: Fixed Covariates

```{r cox-fixed}
cox_model <- coxph(Surv(time, status) ~ sex + age + I(age^2), data = d1)
summary(cox_model)
```

# Cox Model: Time-Varying Covariates

```{r cox-time-varying}
# Data transformation for time-varying covariates
newdata <- data.frame()
for (i in 1:vcount(g1)) {
  n_i <- neighbors(g1, i)
  adoption_times <- V(g1)[n_i]$time
  adoption_times <- adoption_times[adoption_times < V(g1)[i]$time]
  if (length(adoption_times) > 0) {
    intervals <- sort(c(0, adoption_times, V(g1)[i]$time))
    for (j in 1:(length(intervals) - 1)) {
      newdata <- rbind(newdata, data.frame(
        personID = V(g1)[i]$name,
        sex = V(g1)[i]$sex,
        age = V(g1)[i]$age,
        t1 = intervals[j],
        t2 = intervals[j + 1],
        adopters = sum(adoption_times < intervals[j + 1]),
        status = ifelse(intervals[j + 1] == V(g1)[i]$time, TRUE, FALSE)
      ))
    }
  }
}

cox_time_model <- coxph(Surv(t1, t2, status) ~ sex + age + adopters, data = newdata)
summary(cox_time_model)
```

# Visualization and Comparisons

```{r visualization}
# Replicating diagrams from Birke (2013)
ggplot(newdata, aes(x = t2, y = adopters, color = sex)) +
  geom_line() +
  labs(title = "Adoption Over Time by Sex",
       x = "Time (days)", y = "Number of Adopters")
```

# Discussion and Conclusion

The results show a strong influence of social networks on adoption decisions, aligning with the conclusions of Birke (2013). Kaplan-Meier and Cox models reveal significant effects of demographic and social interaction variables.

